Cyclist video evidence of road traffic offences: Preliminary analysis of Operation Snap data and suggestions for a research agenda

### 2024-04-22 paper.qmd
Improve table

```{r}
d_all |>
  count(mode, sort = TRUE) |>
  mutate(percent_records = n / nrow(d_all)) |>
  mutate(percent_records = scales::percent(percent_records)) |>
  arrange(desc(n)) |>
  knitr::kable()
```

>>>>

```{r}
d_all |>
  count(mode, sort = TRUE) |>
  mutate(percent_records = n / nrow(d_all)) |>
  mutate(percent_records = scales::percent(round(percent_records, 3))) |>
  arrange(desc(n)) |>
  knitr::kable(digits = 1)
```
